Final Project Data 205

### 2021-12-14 Draft Final Project1.Rmd
Add files via upload

```{r}
#Create a time series plot
WMATA$hour <- as.numeric(gsub(":.*$", "", WMATA$time))
WMATA$cat <- with(WMATA,  ifelse(hour >= 5 & hour<=11, "morning",
                            ifelse(hour>11 & hour<=16, "evening", "night")))
WMATA
```

## Plot 1
```{r}
p1<-WMATA  %>%
  filter(state %in% c("DC","MD","VA")) %>%
  ggplot(aes(x=state, fill= state))+
  geom_bar()+
  labs(title="Total of Crimes by State/District",x="State/District", y="Total")+
  scale_fill_brewer(palette = "Dark2") + theme_minimal()
p1 + theme_minimal()
```

@@

@@

@@

# Extract the street address from desc using Regex.  Extract crime description also.
df_wmata2 <- df_wmata %>% mutate(street_addr=str_remove(desc, "[[:upper:]]{2,}.+")) %>%
  mutate(crime_desc=str_extract(desc, "[[:upper:]]{2,}.+"))
df_wmata2 <- df_wmata2 %>% mutate(full_addr=paste(street_addr,state))

@@

```{r}
ggplot(diamonds, aes(x=price, y=color, fill=color)) +
```

@@

@@

## 
```{r}

>>>>

```{r}
#Create a time series plot
WMATA$hour <- as.numeric(gsub(":.*$", "", WMATA$time))
WMATA$timeofday <- ifelse(WMATA$hour >= 5 & WMATA$hour<=11, "morning",
                            ifelse(WMATA$hour > 11 & WMATA$hour<=16, "afternoon",
                            ifelse(WMATA$hour >16 & WMATA$hour <=19, "evening", "night"))) 
WMATA
```

## Plot 1
```{r}
p1<-WMATA  %>%
  filter(state %in% c("DC","MD","VA")) %>%
  ggplot(aes(x=year, fill= state))+
  geom_bar()+
  labs(title="Total of Crimes by State/District",x="State/District", y="Total")+
  scale_fill_brewer(palette = "BuPu") + theme_minimal()
p1 + theme_minimal()
```

@@

## Preparing the data (time)
```{r}
d3<- WMATA%>%
  group_by(year, timeofday) %>%
  dplyr::summarize(Freq=n())
```

##Fix Na's 
```{r}
d4 <-na.omit(d3)
```

## Facet
```{r}
 ggplot(data = d4,
        mapping = aes(x = year, y = Freq)) +
     geom_bar(stat="identity") +
     facet_wrap(vars(timeofday)) +
     theme_minimal()
```

@@

## using count 
```{r}
WMATA %>%
  group_by(year,timeofday) %>%
  summarise(n = n()) %>%
  mutate(Freq = n/sum(n))
```

## Time Series

```{r}
sp <- ggplot(WMATA, aes(x=year, )) + geom_point(shape=1)
sp + facet_grid(. ~ cat)
```
##
```{r}
hp <- ggplot(tips, aes(x=total_bill)) + geom_histogram(binwidth=2,colour="white")
```

@@

# Extract the street address from desc using Regex.  Extract crime description also.
df_wmata2 <- WMATA %>% mutate(street_addr=str_remove(desc, "[[:upper:]]{2,}.+")) %>%
  mutate(crime_desc=str_extract(desc, "[[:upper:]]{2,}.+"))
df_wmata2 <- df_wmata2 %>% mutate(full_addr=paste(street_addr,state))

@@

@@

```{r}
library(dplyr)
library(httr)
#library(jsonlite)
library(stringr)
library(tidygeocoder)

# Extract the street address from desc using Regex.  Extract crime description also.
df_wmata2 <- WMATA %>% mutate(street_addr=str_remove(desc, "[[:upper:]]{2,}.+")) %>%
  mutate(crime_desc=str_extract(desc, "[[:upper:]]{2,}.+"))
df_wmata2 <- df_wmata2 %>% mutate(full_addr=paste(street_addr,state))

#Apply the geocode function to get lat/lon values
coordinates <- df_md %>% geocode(full_addr)

coordinates$census_tract <- 0
row_count <- nrow(coordinates)
```

@@

## f
```{r}
